Bringing the Power of eBPF to Open vSwitch

### 2018-10-22 paper.tex
more revise

OVS is widely used in virtualized data center environments as a software
switching layer inside various operating systems, including FreeBSD,
Windows Hyper-V, Solaris and Linux. As shown in
Figure~\ref{ovsintro:fig}, the architecture of OVS consists of two major
components: a slow path and a fast path. OVS begins processing packets
in its datapath, the fast path, shortly after the packet is received by the NIC in the host OS.
The OVS datapath first performs packet parsing to extract relevant protocol
headers from the packet and store it locally in a manner that is efficient for
performing lookups (flow key), then it uses this information to look into the
match/action cache (flow table) and determines what needs to be done for this
packet. If there is no match in the flow table, the datapath passes the packet
from the kernel up to the slow path, \verb+ovs-vswitchd+, which maintains the
full determination of what needs to be executed to modify and forward
the packet correctly.  This process is called packet {\em upcall} and
usually happens at the first packet of a flow seen by the OVS datapath.
If the packet matches in this flow table, then the OVS datapath executes its
corresponding actions from the flow table lookup result and updates its flow
statistics.

@@

                +-------------------+
 slow path      |    ovs-vswitchd   |
                +-----^-------------+
                      |       |flow installation
----------------------|-------|-----------------
 fast path     upcall |       | 
 (datapath)  +----------------v---------+ 
  packets--> | parse, lookup, actions   |  --> output
             +--------------------------+
\end{verbatim}
}
\vspace{-1.0em}
\caption{An example of mirrored packet with outer header containing
the GRE and ERSPAN header, followed by the innter Ethernet frame.}
\label{erspanhdr}
\vspace{-1.0em}
\end{figure}

@@

\subsection{AF\_XDP netdev configuration}
When users attach a AF\_XDP netdev to the OVS bridge, for example, by
issuing the following command:
{
\begin{verbatim}
    ovs-vsctl add-br br0
    ovs-vsctl add-port br0 eth0 -- \
        set int eth0 type="afxdp"
\end{verbatim}
}
ovs-vswitch does the following steps to configure the
AF\_XDP netdev:
\begin{enumerate}
\item Attach a XDP program to the netdev's queue:
The XDP program OVS attaches is fixed and consists
of only a few line of code, which receives the packet and
calls the \texttt{bpf\_redirect\_map()} helper function with
the XSK eBPF maps and key equals zero.

@@

\item Fill the UMEM FILL ring: Get a couple UMEM elements and place into FILL ring.
\end{enumerate}
On the other hand, when a AF\_XDP netdev is detached or closed by user,
ovs-vswitchd closes the XSK socket, free the UMEM memory region, and
unload the eBPF program and map.

% 1 UMEM per XSK per queue, no sharing
%For each netdev, ovs-vswitchd attach XSK to each 
%For each XSK
\subsection{Packet Reception}
In order to properly set-up the RX/TX/FILL/COMPLETION rings, we implement a
UMEM memory management API. Basically, it's a list maintaining the unused elements
in UMEM, called UMEM freelist, and APIs to get/put elements into the list.
\begin{figure}
{\scriptsize
\begin{verbatim}
UMEM: total 8 elements, each has 2K chunk size
                 +-------------------------------+
                 |   |   |   |   |   |   |   |   |
                 +-------------------------------+
            addr:  1   2   3   4   5   6   7  8 
(1) Initial Stat
           -------------------          UMEM freelist
FILL Qu  ...| 1 | 2 | 3 | 4 | ...       {5, 6, 7, 8}
           -------------------
           -------------------
RX ring  ...|   |   |   |   | ...
           -------------------
(2) 4 Packets Arrive
           -------------------          UMEM freelist
FILL Qu  ...|   |   |   |   | ...       {5, 6, 7, 8}
          --------------------
           -------------------
RX ring  ...| 1 | 2 | 3 | 4 | ...
           -------------------
(3) Get 4 free UMEM elemet and refill
           -------------------          UMEM freelist
FILL Qu  ...| 5 | 6 | 7 | 8 | ...       {} 
           -------------------
           -------------------
RX ring  ...| 1 | 2 | 3 | 4 | ...
           -------------------
(4) Pass packets {1, 2, 3, 4} to dpif-netdev
    for parse, lookup, and actions.

@@

\subsection{Performance Evaluation}
All of our performance results use a hardware test bed that consists of
two Intel Xeon E5 2440 v2 1.9GHz servers, each with 1 CPU socket and
8 physical cores with hyperthreading enabled.
One server, the target server, has an Intel 40GbE XL710 single port NIC,
the other server, the source server, has Netronome NFP-4000 40GbE device.
The target server runs the Linux kernel 4.19-rc4, with i40e driver supporting
the AF\_XDP mode.
We installed OVS-AFXDP on the target server, and the other server,
the source server, generates 64-byte single UDP flow packets
at the rate of 19~Mpps using the DPDK library.

For all our experiments, we fuse a microbenchmark program, called xdpsock,
as the baseline to compare with OVS-AFXDP implementation.
xdpsock is an AF\_XDP sample program doing no packet processing, and can be configured
to do simply dropping the packet, rxdrop, or forwarding the packet to the same port as
it receives, l2fwd.
In our testbed, we measured $19Mpps$ for xdpsock-rxdrop and $17Mpps$ for xdpsock-l2fwd.
For OVS-AFXDP, we conduct similar two experiments, but with OVS's OpenFlow rule below:
\begin{itemize}
\item OVS-AFXDP rxdrop: Install a single OpenFlow rule to drop every packets,
e.g.,  \texttt{in\_port=eth1, actions=drop}.
\item OVS-AFXDP l2fwd: Install a single OpenFlow rule to forward packet to the same port
as it receives, e.g., \texttt{in\_port=eth1, actions=set\_fields:eth2->in\_port, output:eth1}.
\end{itemize}

Additionally, AF\_XDP provides three operation modes:
1) XDP\_SKB: works on devices using generic XDP~\cite{genericxdp},
2) XDP\_DRV: works on devices with XDP support.
3) XDP\_DRV ZC (Zero Copy): works on devices with XDP\_XDP zerecopy support.
For all our experiments, we use the XDP\_DRV ZC mode.

When forwarding packets using AF\_XDP with OVS, two CPUs show up
100\% utilitization:
\begin{itemize}
\item ovs-vswitchd: This is the process keeps doing the send and receive steps
in Figure~\ref{afxdprx,afxdptx}.
\item ksoftirqd: This is the kernel software interrupt thread handling the
incoming packets, triggering XDP program to pass to the XSK, and also processing
transmission.
\end{itemize}

Compared to xdpsock, ovs-vswitchd adds on top of it a UMEM memory pool,
and packets parsing, lookup and action execution.
Our initial prototype shows pretty terrible performance, only $0.5Mpps$ rxdrop.
We investigated and our first fix is to enable OVS's PMD-mode,
Poll-Mode-Driver, to the afxdp netdev.

\subsubsection{PMD netdev}
In OVS, a non-pmd mode netdev does packet receiption by putting all the receiving
netdev's file descript together and ovs-vswitch polls them when there is an fd ready
to perform I/O.  As a result, the fd of the XSK is {\em shared} with other fds, and
we observed that the poll system call has pretty high overhead.

Applying OVS's PMD netdev avoids these problems and improving the rxdrop performance
from $0.5Mpss$ to $3Mpps$.  Ideally, receing packets from XSK does not need to context
switch to into kernel as mentioned in steps~\ref{afxdprx}. So an ideal implementation
should show minimal context switches with most of the CPU stays in userspace. 
When enabling PMD netdev for afxdp, ovs-vswitch can be
configured to create a {\em dedicated} thread for the packet I/O.  
In our case, we create a thread for each XSK receive queue which keeps polling
the RX ring for new packets.  Each round of receive polling processes a batch of
packet, up to maximum of 32 packets. In addition, we enable high memory page 1GB to
reduce the page fault overhead.  With the above fixes/optimizations, the rxdrop
performance increases to around $10Mpps$

\subsubsection{Memory Management and Locks}
For every stage of the optimization, we use Linux perf extensively, e.g., perf stat
and perf record/report.  With the above new design, we observe the new bottleneck
is at the UMEM memory pool we introduce to maintain the UMEM freelist, and the
packet metadata allocation, struct dp\_packet, for every receiving packet.
We introduce two major API, umem\_elem\_get(), which gets N free element from the
UMEM freelist, and umem\_elem\_put(), which places back the free UMEM buffer to
the freelist.
producer, consumer
We implemented three data structures of UMEM memory pool as below
to compare their performance
\begin{itemize}
\item list\_head: Similar to Linux kernel's list\_head, each element contains it
UMEM addr, and a next pointer points to next free element. Elements are sparse in
memory. Consumer always takes the first element, head, and producer also place back
from the head of the list.
\item ptr\_ring: Similar to Linux kernel's ptr\_ring, an array of elements are
allocated in continuous memory region, and pointers (head and tail) point for
Consumer takes elements from the tail and when placing back, producer, puts
them into where head pointer points to.
\item ptr\_stack: Similar to ptr\_ring, an array of elements are allocated
in continuous memory region, but both consumer and producer takes elements
from beginning of the array.
\end{itemize}

Although we allocate one UMEM per netdev, there might be multiple queues per
netdev sharing the same UMEM. As a result, the above three data structures
all require a mutex lock before accessing UMEM freelist. Linux perf reports
pthread\_mutex\_lock as one of the top CPU utilization function, and overall
shows around $2Mpps$ overhead for rxdrop experiments.
We change our design by 1) allocating per-queue UMEM region and 2)
allocating one pmd thread per queue. As a result, no lock is needed because
the each queue has only one thread and its own set of UMEM elements.

\subsubsection{Metadat Allocation}
With the above change, Linux perf shows that the packets metadata allocation
takes a lot of CPU cycles, the dp\_packet\_init, dp\_packet\_set\_data.
So instead of allocating packet metadata at packet reception time, we
implement two data structures and compare their performance:
\begin{itemize}
\item Embedding in UMEM buffer: Since we already allocate 2K chunk for each
UMEM buffer, we reserve the first 256-byte in each UMEM element as struct dp\_packet
and initialize the dp\_packet as much as we can at allocation time.
This is similar to the DPDK mbuf design~\cite{dpdkmbuf}, where a single memory buffer
is used for both packet data and metadata.
\item Array on heap: This design simply allocate a continuous memory region
storing an array of packet metadata, and initialize them as much as we can.
\end{itemize}

%complete separation of the allocation of metadata structures from the allocation of packet data buffers.
% see mbuf dpdk https://doc.dpdk.org/guides/prog_guide/mbuf_lib.html
%Embed metadata within a single memory buffer the structure followed by a fixed size area for
% the packet data.
%Use separate memory buffers for the metadata structure and for the packet data.

With the above design change, we found that using the ptr\_stack with
array on heap get the best performance. Largely due to both data structures
have better spatial locality and more batching friendly.
For example, setting up 32 packet metadatas in an array definitely incurs
less cache misses than setting up in 32 elements in UMEM.
And getting 32 free UMEM elements from ptr\_stack has similar benefits.
With the above decision, the OVS rxdrop shows $17Mpps$, only $2Mpps$ less
than the baseline xdpsock rxdrop.

\subsubsection{Batching Send Syscall}
%574.790 M/sec  
We continued measured the performance of OVS-AFXDP l2fwd and.
observed only $4Mpps$, compared to $17Mpps$ baseline xdpsock.
Again, by analysis using perf, we found that the OVS pmd thread under rxdrop
has much fewer context switches compared to the l2fwd, indicating that
the PMD process spends much more time in kernel space than in userspace.
By using strace, we saw that the l2fwd experiement calls sendto system call
at very high frequeuce, because from Figure~\ref{afxdptx}, we design to check
the success of send (step 4) immediately after issusing send (step 3).
We change the design by calling send syscall (step 3) only when TX ring is
closed to full, e.g., when 3/4 ring elements have been used.
In specific case, instead of issuing send syscall for a batch of 32 packets
and making sure they are done, we only issue send when there are 512 outstanding
packets.  With this change, the OVS-AFXDP l2fwd experiment shows around $14Mpps$.

%rxhash

\bibliography{paper.bib}
\bibliographystyle{plain}

>>>>

OVS is widely used in virtualized data center environments as a software
switching layer inside various operating systems, including FreeBSD,
Windows Hyper-V, Solaris and Linux. As shown in
Figure~\ref{ovsintro}, the architecture of OVS consists of two major
components: a slow path and a fast path. OVS begins processing packets
in its datapath, the fast path, shortly after the packet is received by the NIC in the host OS.
The OVS datapath first performs packet parsing to extract relevant protocol
headers from the packet and store it locally in a manner that is efficient for
performing lookups (flow key), then it uses this information to look into the
match/action cache (flow table) and determines what needs to be done for this
packet. If there is no match in the flow table, the datapath passes the packet
from the kernel up to the slow path, \verb+ovs-vswitchd+, which maintains the
full determination of what needs to be executed to modify and forward
the packet correctly.  This process is called packet {\em upcall} and
usually happens at the first packet of a flow seen by the OVS datapath.
If the packet matches in this flow table, then the OVS datapath executes its
corresponding actions from the flow table lookup result and updates its flow
statistics.

@@

                +-------------------+
 slow path      |    ovs-vswitchd   |
                +-----^-------------+
                      |       |flow installation
----------------------|-------|-----------------
 fast path     upcall |       | 
 (datapath)  +----------------v---------------+ 
  packets--> | parse, lookup match, actions   |  --> output
             |        & action table          |
             +--------------------------------+
\end{verbatim}
}
\vspace{-1.0em}
\caption{
The forwarding plane of OVS consists of two components;
ovs-vswitch handles the complexity of the OpenFlow protocol, and the
datapath acts as a caching layer to optimize the performance.  A flow
missed by the match/action table in the datapath triggers an {\em
upcall}, which forwards the information to ovs-vswitchd.  ovs-vswitchd
installs an appropriate flow entry into the datapath's match/action table.}
\label{ovsintro}
\vspace{-1.0em}
\end{figure}

@@

\subsection{AF\_XDP netdev configuration}
When users attach a AF\_XDP netdev to an OVS bridge, for example, by
issuing the following commands:
{\small
\begin{verbatim}
    ovs-vsctl add-br br0
    ovs-vsctl add-port br0 eth0 -- \
        set int eth0 type="afxdp"
\end{verbatim}
}
ovs-vswitch does the following steps to bring up the
AF\_XDP netdev:
\begin{enumerate}
\item Attach a XDP program to the netdev's queue:
The XDP program OVS attaches is fixed and consists
of only a few line of code, which receives the packet and
calls the \texttt{bpf\_redirect\_map()} helper function with
the XSK eBPF maps and key equals zero.

@@

\item Populate the UMEM FILL ring: Get a couple UMEM elements and place into FILL ring.
\end{enumerate}
On the other hand, when a AF\_XDP netdev is detached or closed by user,
ovs-vswitchd closes the XSK socket, free the UMEM memory region, and
unload the eBPF program and map.

In order to properly set-up the RX/TX/FILL/COMPLETION rings, we implement a
UMEM memory management API. Basically, it's a list maintaining the unused elements
in UMEM, called UMEM freelist, and function calls to get/put elements into the list.
\subsection{Packet Reception}
\begin{figure}
{\scriptsize
\begin{verbatim}
UMEM: total 8 elements, each has 2K chunk size
                 +-------------------------------+
                 |   |   |   |   |   |   |   |   |
                 +-------------------------------+
            addr:  1   2   3   4   5   6   7  8 
(1) Initial Stat
           -------------------          UMEM freelist
FILL Qu  ...| 1 | 2 | 3 | 4 | ...       {5, 6, 7, 8}
           -------------------
           -------------------
RX ring  ...|   |   |   |   | ...
           -------------------
(2) 4 Packets Arrive
           -------------------          UMEM freelist
FILL Qu  ...|   |   |   |   | ...       {5, 6, 7, 8}
          --------------------
           -------------------
RX ring  ...| 1 | 2 | 3 | 4 | ...
           -------------------
(3) Get 4 free UMEM elemet and refill
           -------------------          UMEM freelist
FILL Qu  ...| 5 | 6 | 7 | 8 | ...       {} 
           -------------------
           -------------------
RX ring  ...| 1 | 2 | 3 | 4 | ...
           -------------------
(4) Pass packets {1, 2, 3, 4} to dpif-netdev
    for parse, lookup, and actions.

@@

\subsection{Performance Evaluation}
All of our performance results use a hardware test bed that consists of
two Intel Xeon E5 2440 v2 1.9GHz servers, each with 1 CPU socket and
8 physical cores with hyperthreading enabled.
One server, the target server, has an Intel 40GbE XL710 single port NIC,
and the other server, the source server, has Netronome NFP-4000 40GbE device.
The target server runs the Linux kernel 4.19-rc4, with i40e driver supporting
the AF\_XDP mode.
We installed OVS-AFXDP on the target server, and the other server,
the source server, generates 64-byte single UDP flow packets
at the rate of 19~Mpps using the DPDK library.
On the target server, we also disable the spectre and meltdown fixes.

For all our experiments, we fuse a microbenchmark program, called xdpsock,
as the baseline to compare with OVS-AFXDP implementation.
xdpsock is an AF\_XDP sample program doing no packet processing, and can be configured
to do simply dropping all packets, rxdrop, or forwarding the packet to the same port as
it receives, l2fwd.
In our testbed, we measured $19Mpps$ for xdpsock-rxdrop and $17Mpps$ for xdpsock-l2fwd.
For OVS-AFXDP, we conduct similar two experiments, but with OVS's OpenFlow rule installed as
below:
\begin{itemize}
\item OVS-AFXDP rxdrop: Install a single OpenFlow rule to drop every packets,
e.g.,  \texttt{in\_port=eth1, actions=drop}.
\item OVS-AFXDP l2fwd: Install a single OpenFlow rule to forward packet to the same port
as it receives, e.g., \texttt{in\_port=eth1, actions=set\_fields:eth2->in\_port, output:eth1}.
\end{itemize}

Additionally, AF\_XDP provides three operation modes:
XDP\_SKB: works on devices using generic XDP~\cite{genericxdp},
XDP\_DRV: works on devices with XDP support, and
XDP\_DRV ZC (Zero Copy): works on devices with XDP\_XDP zerecopy support.
For all our experiments, we use the XDP\_DRV ZC mode.

\subsubsection{PMD netdev}
Our initial prototype shows pretty terrible performance, only $0.5Mpps$ for rxdrop.
We observe that when dropping/forwarding packets under OVS-AFXDP, two CPUs show up
100\% utilitization:
\begin{itemize}
\item ovs-vswitchd: This is the process keeps doing the send and receive steps
in Figure~\ref{afxdprx} and~\ref{afxdptx}.
\item ksoftirqd/core\_id: This is the kernel software interrupt thread handling the
incoming packets, triggering XDP program to pass packets to the XSK, and also
processing transmission.
\end{itemize}
\mycomment{Compared to xdpsock, ovs-vswitchd adds on top of it a UMEM memory pool,
and packets parsing, lookup and action execution.}
We investigate using Linux perf and our first fix is to enable OVS's PMD-mode,
Poll-Mode-Driver, to the afxdp netdev.

In OVS, a non-pmd mode netdev does packet receiption by putting all the receiving
netdev's file descriptors, fds, together and ovs-vswitchd polls them when there is an fd
ready to perform I/O.  As a result, the fd of the XSK is {\em shared} with other fds, and
we observed that the poll system call has pretty high overhead.

Applying OVS's PMD netdev avoids these problems and improving the rxdrop performance
from $0.5Mpss$ to $3Mpps$.  Ideally, receing packets from XSK should not need to context
switch to into kernel as mentioned in steps~\ref{afxdprx}. So an ideal implementation
should show minimal context switches with most of the CPU time stays in userspace. 
When enabling PMD netdev for afxdp, ovs-vswitch can be
configured to create a {\em dedicated} thread for the packet processing.
In OVS-AFXDP, we create a thread for each XSK's receive queue and the thread keeps polling
the RX ring for new packets.  Each round of receive polling processes a batch of
packet, up to maximum of 32 packets. In addition, we enable 1GB huge memory page support
to reduce the page fault overhead.  With the above fixes/optimizations, the rxdrop
performance increases to around $10Mpps$

\subsubsection{Memory Management and Locks}\label{memorym}
For every stage of the optimization, we use Linux perf extensively, e.g., perf stat
and perf record/report.  With the above new design, we observe the new bottleneck
is at the UMEM memory pool APIs we introduce to maintain the UMEM freelist, as well as the
packet metadata allocation, struct dp\_packet, for every receiving packet.
We introduce two major API, umem\_elem\_get(), which gets N free element from the
UMEM freelist, and umem\_elem\_put(), which places back the free UMEM buffer to
the freelist, similar to the concept of producer (put) and consumer (get).
We implemented three different data structures of UMEM memory pool as below
to compare their performance.
\begin{itemize}
\item list\_head: Similar to Linux kernel's list\_head, each element contains its
UMEM element address, and a next pointer points to next free element.
Due to the nature of list\_head, elements are sparse in memory.
Consumer always takes the first element, head, and producer also place back
from the head of the list.
\item ptr\_ring: Similar to Linux kernel's ptr\_ring, an array of elements are
allocated in continuous memory region.
Consumer takes elements from the tail pointer and when placing back, producer, puts
them into where head pointer points to.
\item ptr\_stack: Similar to ptr\_ring, an array of elements are allocated
in continuous memory region, but both consumer and producer takes elements
from beginning of the array.
\end{itemize}

Although we allocate one UMEM per netdev, there might be multiple queues per
netdev sharing the same UMEM. As a result, the above three data structures
require a mutex lock before accessing UMEM freelist. Linux perf reports
pthread mutex lock related APIs as one of the top CPU utilization function.
We change our design by 1) allocating per-queue UMEM region and 2)
allocating one pmd thread per queue. As a result, no lock is needed because
the each queue has only one thread and its own set of UMEM elements.

\subsubsection{Metadata Pre-allocation}
Moving forward, Linux perf shows that the packets metadata allocation
takes a lot of CPU cycles, i.e.,  dp\_packet\_init(), dp\_packet\_set\_data().
So instead of allocating packet metadata at packet reception time, we
implemented two data structures and compare their performance:
\begin{itemize}
\item Embedding in packet buffer: Since we already allocate 2K chunk for each
UMEM packet buffer, we reserve the first 256-byte in each UMEM element as struct dp\_packet
and initialize the dp\_packet as much as we can at allocation time.
This is similar to the DPDK mbuf design~\cite{dpdkmbuf}, where a single memory buffer
is used for both packet data and metadata.
\item Separate from packet buffer: This design simply allocate a continuous memory region
storing an array of packet metadata, and initialize them as much as we can.
\end{itemize}

%complete separation of the allocation of metadata structures from the allocation of packet data buffers.
% see mbuf dpdk https://doc.dpdk.org/guides/prog_guide/mbuf_lib.html
%Embed metadata within a single memory buffer the structure followed by a fixed size area for
% the packet data.

With the above design change, we found that using the ptr\_stack in section~\ref{memorym} with
separate from packet buffer design yields the best performance. Largely due to both data structures
have better spatial locality and more batching friendly, when all data are allocated together.
For example, setting up 32 packet metadatas in an array definitely incurs
less cache misses than setting up in 32 elements in UMEM.
And getting 32 free UMEM elements from ptr\_stack has similar benefits.
With the above decision, the OVS rxdrop shows around $19Mpps$, closed
to the baseline xdpsock rxdrop performance.

\subsubsection{Batching Send Syscall}
%574.790 M/sec  
We continued measuring the performance of OVS-AFXDP l2fwd and
observed only $4Mpps$, compared to $17Mpps$ baseline xdpsock-l2fwd.
We found that the OVS pmd thread under rxdrop
has much fewer context switches compared to the l2fwd, indicating that
the pmd process spends much more time in kernel space than in userspace.
By using strace, we saw that the OVS-AFXDP l2fwd experiement calls sendto system call
at very high frequeuce, because from Figure~\ref{afxdptx}, we design to check
the success of send (step 4) immediately after issusing send (step 3).
We change the design by calling send syscall (step 3) only when TX ring is
closed to full, e.g., when 3/4 ring elements have been used.
In specific case, instead of issuing send syscall for a batch of 32 packets
and making sure they are done, we only issue send when there are 512 outstanding
packets.  With this change, the OVS-AFXDP l2fwd experiment shows around $14Mpps$.

\subsubsection{Summary}
In summary, with the above design and optimization, OVS-AFXDP shows
\begin{table}
\centering
\small
\begin{tabular}{|c | c | c|}
\hline
 {\bf Projects} & {\bf xdpsock } & {\bf OVS-AFXDP} \\ \hline\hline
  rxdrop & 19Mpps & 19Mpps \\ \hline
  l2fwd  & 17Mpps & 14Mpps \\ \hline
  \end{tabular}
\caption{\footnotesize
Performance comparison of the xdpsock and and OVS-AFXDP.
}
\label{compare}
\end{table}
Although there are still rooms for improvement, we are now working on
making the patch upstream to the OVS code base for more people to use.

\section{Conclusion}
\bibliography{paper.bib}
\bibliographystyle{plain}
